Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-03 analysis/paper/paper.qmd
the chunk label needs fig-xxx for captions to work

```{r}
#| label: tcsa-all-sp
#| fig-cap: Distribution of TCSA values for all Korean stemmed points in the current dataset. Shaded boxes show TSCA ranges for various weapon types.
#| fig-width:   4.5
#| fig-height:  4.4

@@

To gain a general idea of the role of stemmed points, we calculated TCSA for all stemmed points. @tcsa-all-sp shows the mean TCSA is `r round(mean(tcsa$min_tcsa), digits=1)`, and standard deviation of TCSA is `r round(sd(tcsa$min_tcsa), digits=1)`. Overall we see a wide variation of TCSA values in this boxplot. According to -@lombard2021variation TCSA ranges (Table 1), Korean stemmed points are mostly in the categories of javelins and thrusting spear tips, with smaller numbers as dart tips and arrowheads. Among the weapon-tip types, only poison arrowheads appear to be absent from these Korean assemblages.

>>>>

```{r}
#| label: fig-tcsa-all-sp
#| fig-cap: Distribution of TCSA values for all Korean stemmed points in the current dataset. Shaded boxes show TSCA ranges for various weapon types.
#| fig-width:   4.5
#| fig-height:  4.4

@@

To gain a general idea of the role of stemmed points, we calculated TCSA for all stemmed points. @fig-tcsa-all-sp shows the mean TCSA is `r round(mean(tcsa$min_tcsa), digits=1)`, and standard deviation of TCSA is `r round(sd(tcsa$min_tcsa), digits=1)`. Overall we see a wide variation of TCSA values in this boxplot. According to -@lombard2021variation TCSA ranges (Table 1), Korean stemmed points are mostly in the categories of javelins and thrusting spear tips, with smaller numbers as dart tips and arrowheads. Among the weapon-tip types, only poison arrowheads appear to be absent from these Korean assemblages.
